Refactoring the \texttt{nls()} function in R

### 2022-06-21 RefactoringNLS/RefactoringNLS.Rmd
bracket mismatch

`nls()` is the tool in base R (the distributed software package from [CRAN](https://cran.r-project.org)
for estimating nonlinear statistical models. The function dates to the 1980s and the work related
to @bateswatts in S (see https://en.wikipedia.org/wiki/S_%28programming_language%29).

>>>>

`nls()` is the tool in base R, the primary software software distribution
from the Comprehensive R Archive Network (https://cran.r-project.org)
for estimating nonlinear statistical models. The function dates to the 1980s and the work
related to @bateswatts in S (see https://en.wikipedia.org/wiki/S_%28programming_language%29).

### 2022-06-21 RefactoringNLS/RefactoringNLS.tex
bracket mismatch

\texttt{nls()} is the tool in base R (the distributed software package
from \href{https://cran.r-project.org}{CRAN} for estimating nonlinear
statistical models. The function dates to the 1980s and the work related
to D. M. Bates and Watts (\protect\hyperlink{ref-bateswatts}{1988}) in S
(see
\url{https://en.wikipedia.org/wiki/S_\%28programming_language\%29}).

@@

\begin{verbatim}
## nlsr object: x 
## residual sumsquares =  0  on  11 observations
##     after  1    Jacobian and  1 function evaluations
##   name            coeff          SE       tstat      pval      gradient    JSingval   
## a                     -3            NA         NA         NA           0       26.49  
## b                      5            NA         NA         NA           0       9.615  
## c                    0.5            NA         NA         NA           0       2.466  
## r                    0.7            NA         NA         NA           0      0.1098  
## m                      1            NA         NA         NA           0   1.118e-16
\end{verbatim}

@@

\begin{verbatim}
## nlsr object: x 
## residual sumsquares =  9.4726  on  12 observations
##     after  16    Jacobian and  17 function evaluations
##   name            coeff          SE       tstat      pval      gradient    JSingval   
## b1                     2U           NA         NA         NA           0       23.35  
## b2               4.43325            NA         NA         NA   1.832e-10           0  
## b3                     3U           NA         NA         NA           0           0
\end{verbatim}

>>>>

\texttt{nls()} is the tool in base R, the primary software software
distribution from the Comprehensive R Archive Network
(\url{https://cran.r-project.org}) for estimating nonlinear statistical
models. The function dates to the 1980s and the work related to D. M.
Bates and Watts (\protect\hyperlink{ref-bateswatts}{1988}) in S (see
\url{https://en.wikipedia.org/wiki/S_\%28programming_language\%29}).

@@

\begin{verbatim}
## nlsr object: x 
## residual sumsquares =  0  on  11 observations
##     after  1    Jacobian and  1 function evaluations
##   name            coeff          SE       tstat      pval      gradient    JSingval   
## a                     -3             0       -Inf          0           0       26.49  
## b                      5             0        Inf          0           0       9.615  
## c                    0.5             0        Inf          0           0       2.466  
## r                    0.7             0        Inf          0           0      0.1098  
## m                      1             0        Inf          0           0   1.949e-09
\end{verbatim}

@@

\begin{verbatim}
## nlsr object: x 
## residual sumsquares =  9.4726  on  12 observations
##     after  16    Jacobian and  17 function evaluations
##   name            coeff          SE       tstat      pval      gradient    JSingval   
## b1                     2U           NA         NA         NA           0       23.35  
## b2               4.43325            NA         NA         NA   1.015e-10           0  
## b3                     3U           NA         NA         NA           0           0
\end{verbatim}
